---
title: "R Notebook"
output: blastula::blastula_email



---


```{r echo=FALSE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) # data manipulation and visualization
library(dplyr) # data manipulation
library(lubridate) # dates
library(data.table) # formatting 
library(knitr) # kniting 
library(ggplot2) # visualizations
library(matrixStats) # stats
library(plotly) # visualizations
library(zoo) # working w/time series data
library(blastula) #compose and send emails 
library(ggpubr) # setting multiple plots on one page

# get functions
source("function.R")
# get data
source("load_data.R")

# Get a nicely formatted date/time string
date_time <- add_readable_time()

```


Good Morning:

This is your daily COVID-19 report, sent on `r date_time`. Shown below is a current **draft** in continual development and error checking. Please feel free to reach out with suggestions or issues!

---

### USA overall

> `r usa_body`

#### 7-day moving average of new cases in the US (`r first_day` to `r most_recent`)
```{r echo=FALSE, warning=FALSE}

usa_cases <- mavg_plot_func(daily_new)

usa_cases <-
  add_ggplot(plot_object = usa_cases)
usa_cases

```

---

### Los Angeles County, CA

> `r la_body`


#### 7-day moving average of new cases in Los Angeles County (`r min(la$date)` to `r max(la$date)`)

```{r echo=FALSE, warning=FALSE}
la <- mavg_plot_func(la)

la <-
  add_ggplot(plot_object = la)
la
```

---

### New York City, NY

> `r nyc_body`


#### 7-day moving average of new cases in New York City (`r min(nyc$date)` to `r max(nyc$date)`)

```{r echo=FALSE, warning=FALSE}
nyc <- mavg_plot_func(nyc)

nyc <-
  add_ggplot(plot_object = nyc)
nyc
```

---

### Chicago (Cook County), IL

> `r chicago_body`


#### 7-day moving average of new cases in Chicago (Cook County) (`r min(ck$date)` to `r max(ck$date)`)

```{r echo=FALSE, warning=FALSE}
ck <- mavg_plot_func(ck)

ck <-
  add_ggplot(plot_object = ck)
ck
```


---

### Boston (Suffolk County), MA

> `r boston_body`


#### 7-day moving average of new cases in Boston (Suffolk County) (`r min(sf$date)` to `r max(sf$date)`)

```{r echo=FALSE, warning=FALSE}
sf <- mavg_plot_func(sf)

sf <-
  add_ggplot(plot_object = sf)
sf
```

---

### Hong Kong

> `r hk_body`


#### 7-day moving average of new cases in Hong Kong (`r min(hk$date)` to `r max(hk$date)`)

```{r echo=FALSE, warning=FALSE}
hk <- mavg_plot_func(hk)

hk <-
  add_ggplot(plot_object = hk)
hk
```

